---
title: 'Beneath the Surface: Chart Appendix Seminar'
author: "Catherine Taylor"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Correlation Surface Charts

Rolling 1 year (260 day) correlation coefficients across each maturity on the inflation swap curve. 
Each maturity is measured in forward space (1y1y, 1y2y, 1y3y...1y30y)

## 1.1 ERI

```{r echo=FALSE, message=FALSE, warning=FALSE}


library(shiny)
library(plotly)
library(ggplot2)
library(readxl)
library(tidyverse)
library(zoo)
library(dplyr)
library(data.table)
library(tidyquant)

#library(xlsx)

source("N:/328890/Inflation markets/Inflation Function Library.R")
Inflation_data_final <- read_excel("N:/320562/Inflation/2019Q3_note/Data/inf_dt_final.xlsx", sheet = "dt")
#Inflation_data_date <- read_excel("N:/320562/Inflation/2019Q3_note/Data/inf_dt_final.xlsx", sheet = "dt")
#Inflation_data_final <- cbind(Inflation_data_date[ ,1], Inflation_data_final[ ,2:112])

Correlation_data_final <- read_excel("N:/328890/Inflation markets/Final note/Correlations.xlsx", sheet = "R import")

# Correlation surface charts

Correl_fundamentals <- Correlation_data_final[ ,c(1:36, 78:82)]

# ERI
ERI <- Correl_fundamentals[ ,c(1:36, 39)]
ERI <- ERI[ ,-c(3:6)]
ERI <- na.omit(ERI)

ERI_corr <- function(i) {
  Corr <- runCor(ERI$eri, ERI[ ,i], n=260, cumulative = F, use = "all.obs")
  return(Corr)
}

ERI_matrix <- sapply(2:31, ERI_corr)

# Plot surface
dates <- ERI$...1
mats <- c(1:30)

plot_ly(x=mats, y= dates, z= ERI_matrix) %>% add_surface(colorscale = "YlGnBu",
  contours = list(
    z = list(
      show=TRUE,
      usecolormap=TRUE,
      highlightcolor="#ff0000",
      project=list(z=TRUE)
    ) ) ) %>%
  layout(title = "ERI correlation surface (1 year window)",
         
         scene = list(
           
           xaxis = list(title="Spot maturity (x)" ), 
           yaxis = list(title="Date (y)"),
           zaxis = list(title="Rho (z)")
         ) ) 

```

## 1.2 Brent

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Brent
Brent <- Correl_fundamentals[ ,c(1:36, 37)]
Brent <- Brent[ ,-c(3:6)]
Brent <- na.omit(Brent)

Brent_corr <- function(i) {
  Corr <- runCor(Brent$brent_usd, Brent[ ,i], n=260, cumulative = F, use = "all.obs")
  return(Corr)
}

Brent_matrix <- sapply(2:31, Brent_corr)

# Plot surface
dates <- Brent$...1
mats <- c(1:30)

plot_ly(x=mats, y= dates, z= Brent_matrix) %>% add_surface(colorscale = "YlGnBu",
                                                           contours = list(
                                                             z = list(
                                                               show=TRUE,
                                                               usecolormap=TRUE,
                                                               highlightcolor="#ff0000",
                                                               project=list(z=TRUE)
                                                             ) ) ) %>%
  layout(title = "Brent correlation surface (1 year window)",
         
         scene = list(
           
           xaxis = list(title="Spot maturity (x)" ), 
           yaxis = list(title="Date (y)"),
           zaxis = list(title="Rho (z)")
         ) ) 

```

## 1.3 FTSE

```{r echo=FALSE, message=FALSE, warning=FALSE}
# FTSE
FTSE <- Correl_fundamentals[ ,c(1:36, 41)]
FTSE <- FTSE[ ,-c(3:6)]
FTSE <- na.omit(FTSE)

#plot(Brent$brent_usd, type="l")

FTSE_corr <- function(i) {
  Corr <- runCor(FTSE$uk_foc_ftse,FTSE[ ,i], n=260, cumulative = F, use = "all.obs")
  return(Corr)
}

FTSE_matrix <- sapply(2:31, FTSE_corr)

# Plot surface
dates <- FTSE$...1
mats <- c(1:30)

plot_ly(x=mats, y= dates, z= FTSE_matrix) %>% add_surface(colorscale = "YlGnBu",
                                                           contours = list(
                                                             z = list(
                                                               show=TRUE,
                                                               usecolormap=TRUE,
                                                               highlightcolor="#ff0000",
                                                               project=list(z=TRUE)
                                                             ) ) ) %>%
  layout(title = "FTSE correlation surface (1 year window)",
         
         scene = list(
           
           xaxis = list(title="Spot maturity (x)" ), 
           yaxis = list(title="Date (y)"),
           zaxis = list(title="Rho (z)")
         ) ) 


```


## 1.4 ESI

```{r echo=FALSE, message=FALSE, warning=FALSE}

# ESI correlation
Correl_fundamentals <- Correlation_data_final[ ,c(1:36, 78:82, 107)]

ESI <- Correl_fundamentals[ ,c(1:36, 42)]
ESI <- ESI[ ,-c(3:6)]
ESI <- na.omit(ESI)

#plot(Brent$brent_usd, type="l")

ESI_corr <- function(i) {
  Corr <- runCor(ESI$cesigbp, ESI[ ,i], n=260, cumulative = F, use = "all.obs")
  return(Corr)
}

ESI_matrix <- sapply(2:31, ESI_corr)

# Plot surface
dates <- ESI$...1
mats <- c(1:30)

plot_ly(x=mats, y= dates, z= ESI_matrix) %>% add_surface(colorscale = "YlGnBu",
                                                           contours = list(
                                                             z = list(
                                                               show=TRUE,
                                                               usecolormap=TRUE,
                                                               highlightcolor="#ff0000",
                                                               project=list(z=TRUE)
                                                             ) ) ) %>%
  layout(title = "ESI correlation surface (1 year window)",
         
         scene = list(
           
           xaxis = list(title="Spot maturity (x)" ), 
           yaxis = list(title="Date (y)"),
           zaxis = list(title="Rho (z)")
         ) ) 
```

# 2. Price Surface Chart

RPI inflation swap rate across the inflation swap curve over time.
Each maturity is measured in forward space (1y1y, 1y2y, 1y3y...1y30y)

```{r echo=FALSE, message=FALSE, warning=FALSE}

Inflation_data_numeric <- read_excel("N:/320562/Inflation/2019Q3_note/Data/inf_dt_final.xlsx", sheet = "dt", col_types = "numeric")

price_matrix <- Inflation_data_numeric[ ,c(7:36)]

price_matrix <- as.matrix(price_matrix)

dates <- Correl_fundamentals$...1

plot_ly(x=mats, y= dates, z= price_matrix) %>% add_surface(colorscale = "YlGnBu",
                                                         contours = list(
                                                           z = list(
                                                             show=TRUE,
                                                             usecolormap=TRUE,
                                                             highlightcolor="#ff0000",
                                                             project=list(z=TRUE)
                                                           ) ) ) %>%
  layout(title = "Price Surface",
         
         scene = list(
           
           xaxis = list(title="Spot maturity (x)" ), 
           yaxis = list(title="Date (y)"),
           zaxis = list(title="Price (z)")
         ) ) 

```

# 3. Forward Surface Chart

RPI inflation swap price forward curve at each spot maturity across the spot curve 

eg. x=2 y=2 : 2 year rate, 2 years forward

## 3.1 12 November 2019

```{r echo=FALSE, message=FALSE, warning=FALSE}

forwards = c(0:10)
mats = c(1,2,3,4,5,6,7,8,9,10,12,15,20,25,30,40,50)
Inflation_data <- read_excel("N:/328890/Inflation markets/Inflation forward matrix.xlsx",sheet = "Sheet2")
source("N:/328890/Inflation markets/Inflation Function Library.R")
PlotSurface(2573)

```

## 3.3 30 May 2016 (pre-referendum)

```{r echo=FALSE, message=FALSE, warning=FALSE}

forwards = c(0:10)
mats = c(1,2,3,4,5,6,7,8,9,10,12,15,20,25,30,40,50)
Inflation_data <- read_excel("N:/328890/Inflation markets/Inflation forward matrix.xlsx",sheet = "Sheet2")
source("N:/328890/Inflation markets/Inflation Function Library.R")
PlotSurface(1674)

```


## 3.4 31 October 2016 (post referendum)

```{r echo=FALSE, message=FALSE, warning=FALSE}

forwards = c(0:10)
mats = c(1,2,3,4,5,6,7,8,9,10,12,15,20,25,30,40,50)
Inflation_data <- read_excel("N:/328890/Inflation markets/Inflation forward matrix.xlsx",sheet = "Sheet2")
source("N:/328890/Inflation markets/Inflation Function Library.R")
PlotSurface(1784)

```
